---
title: "dominatRData"
author: "Simon Lizarazo, Ethan Chen, Rajendra K C, Kevin Van Bortle"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{Introduction to dominatR}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
library(knitr)
opts_chunk$set(
        collapse = TRUE,
        comment = "#>", 
        fig.align = 'center',
        warning = FALSE, 
        message = FALSE
)


library(dominatRData)

```

```{r setup}
library(dominatRData)
```

## Overview

This package provides supplemental datasets and files for use with
`dominatR`. For more information on how to use these data, please refer
to the `dominatR` vignette.

The data is used for specific examples, such as three-way (triangle)
visualization of RNA polymerase I, II, and III genomic occupancy
dominance at enzyme-specific gene targets [(Rajendra K C et al., 2024
Molecular
Cell)](https://www.sciencedirect.com/science/article/pii/S1097276524007718?dgcid=author),
or such as 19-way (circular) visualization of tissue-specific gene
accessibility patterns at canonical RNA Pol III-transcribed genes
[(Simon Lizarazo et al., 2025 bioRxiv
preprint)](https://www.biorxiv.org/content/10.1101/2025.08.28.672650v1).

### Installation

To install this package, start R and enter:

```{r installation, eval = FALSE}
library(BiocManager)

BiocManager::install('dominatRData')
```

### From Rajendra K C et al

```{r chun1}
data("rnapol_counts")
head(rnapol_counts)
data("rnapol_score")
head(rnapol_score)
```

### From Simon Lizarazo et al 2025

```{r chun2}

data("atac_tissue_counts")
head(atac_tissue_counts)
data("atac_tissue_score")
head(atac_tissue_score)
```

```{r}
sessionInfo()
```
